\documentclass{article}

\usepackage[margin=1.5in]{geometry}
\usepackage[dvipsnames]{xcolor}
\title{\textbf{Sales and Marketing for "Sadabahar"}}
\author{Chelsy Gangwar, 19112012}
\date{\today}

\begin{document}
\maketitle

\section{Introduction}

\setlength{\parskip}{1em}

\large In this Venture we’ll look at the Marketing strategies which will be used of “Sadabahar”. So, it seems very exciting to work on such topic which is related to our daily life. As we’re all aware of why it is so much important for us and what are the benefits of planting trees and plants. 
\setlength{\parskip}{1em}

\large Coming to the Marketing Strategies which we’ll require to take our venture at a reputed position will be discussed in this paper and what all things that are required for marketing of this particular team/venture.

\setlength{\parskip}{1em}

\large What is Marketing?

\large It refers to different types of activities that a company/team needs to do to promote their selling or buying of a service or product. Marketing includes selling of goods, advertising the product and delivering it to the customers.

\setlength{\parskip}{1em}

\section{Types of Marketing are: }
\begin{itemize}
    \item {\textbf{e - Marketing}} - E-marketing is an advertising discipline that includes all marketing activities conducted by a business online using an electronic device or the internet. Other names for this type of marketing include internet marketing, online marketing, digital marketing or web marketing.
    \item {\textbf{Service Marketing}} - Service marketing is the marketing and selling of intangible products (non-physical products). Services comprise all of those personal facilities which we require from time to time like; medical care, education, renting of living spaces and vehicles, hair cut, spas, musical concerts, dance classes, etc.
    \item {\textbf{Social Marketing}} - Social marketing is an approach used to develop activities aimed at changing or maintaining people's behaviour for the benefit of individuals and society as a whole. For example, it might encourage people to reduce their consumption of fast food or alcohol, increase their consumption of organic food, and encourage a healthy lifestyle in the health sector.
    \item {\textbf{Green Marketing}} - Green marketing refers to the practice of developing and advertising products based on their real or perceived environmental sustainability. When a company's green marketing activities are not substantiated by significant investments or operational changes, they may be criticized for false or misleading advertising.
    \item {\textbf{Holistic Marketing}} - Holistic marketing considers a business and all its parts. It sees a business as one entirety. For example where does a business fit into the broader economy. And how does it impact the lives of its customers. Think of the human body that can only function when all parts are working together.
\end{itemize}

\setlength{\parskip}{1em}

\section{B2B Marketing Strategies:}
\begin{itemize}
    \item Content Marketing
    \item Inbound Marketing
    \item Social Media Marketing
    \item Search Engine Marketing
    \item Account Based Marketing(ABM) and Re-targeting
    \item Conversational Marketing
    \item Industry Events
\end{itemize}

\section{B2C Marketing Strategies:}
\begin{itemize}
    \item Social Network and Viral Marketing
    \item Internet Marketing
    \item Email Marketing
    \item Direct Selling
    \item Point of Purchase (POP) Marketing
    \item Paid Media Advertising
\end{itemize}


\end{document}